Networked Character Devices

### 2011-12-09 report/presentation.tex
Added a few images and slides, updated ref with full auther names

% Combine Architecture and System?
\section{Architecture}

@@

\begin{itemize}
\item Supports exporting a single character device from the server
\item Supports importing a single character device on the client
\item Supports open, close, read, and write calls
\item Supports basic Linux udev operation for automatic node
  creation on client
\item Tested with various ``real'' and device files
\end{itemize}

@@

\begin{itemize}
\item Multi-device, multi-server client-side import support
\item Multi-device server-side export support
\item Support for exclusive use and protection of exported devices
\item Support for ioctl calls
\item Support for providing and obtaining metadata for exported
  devices
\item Support for ``advertisement'' of available exported devices
\item Support for integrating imported devices into other kernel
  subsystems (human interface subsystem, audio subsystem, etc)
\item Addition of ``NCD-admin'' utilities for managing and administering
  NCD system
\item Addition of graceful connect and disconnect handling in real-time
\end{itemize}

@@

\begin{itemize}
\item Divorces peripherals from the computers to which they are
  attached
\item Allows simple creation of a ``Device Server''
\item Extends the ``Everything Is A File'' -nix Philosophy
\item Allows more efficient use of devices
\item Allows devices to be networked in a generalized, uniform manner
\end{itemize}

@@

\begin{itemize}
\item Does not work well when Character Device is not the exclusive
  device interface
  \begin{itemize}
  \item Many modern day devices interface directly with other
    in-kernel function, interfaces, and APIs
  \item procfs and sysfs provide additional device interface points
  \item Socket interfaces (netlink, etc) provide alternative to file
    system interfaces
  \end{itemize}
\item Requires exported devices to be ``de-integrated'' from host system
\item Requires QOS guarantees and high guilty network connection
\end{itemize}

@@

\begin{itemize}
\item Quick, cheap, and simple ad-hoc network KVM systems
\item Remote, networked web-cams, scanners, printers, etc
\item Basis of ``protocol''-over-Ethernet systems (USB-over-Ethernet,
  SATA-over-Ethernet, Etc)
\item Basis of redundant, ``cloud-like'' device pools
\item Basis of peripheral cluster systems (GPU Clusters, RNG Clusters,
  Etc)
\end{itemize}

@@

\begin{itemize}
\item Add multi-device, multi-server support
\item Add kernel sub-system handler layer (HID, etc)
\item Add device protection and removal capabilities to server system
\item Add advertisement protocol
\item Consider removing networking code from client kernel module
\end{itemize}

@@

\section{Bibliography}
%---Bibliography---%
\begin{frame}{\bf Bibliography}

>>>>

\section{Architecture}

@@

  \begin{itemize}
  \item<1-> Supports exporting a single character device from the server
  \item<2-> Supports importing a single character device on the client
  \item<3-> Supports open, close, read, and write calls
  \item<4-> Supports basic Linux udev operation for automatic node
    creation on client
  \item<5-> Tested with various ``real'' and device files
  \end{itemize}

@@

\begin{itemize}
\item<1-> Multi-device, multi-server client-side import support
\item<2-> Multi-device server-side export support
\item<3-> Support for exclusive use and protection of exported devices
\item<4-> Support for ioctl calls
\item<5-> Support for providing and obtaining metadata for exported
  devices
\item<6-> Support for ``advertisement'' of available exported devices
\item<7-> Support for integrating imported devices into other kernel
  subsystems (human interface subsystem, audio subsystem, etc)
\item<8-> Addition of ``NCD-admin'' utilities for managing and administering
  NCD system
\item<9-> Addition of graceful connect and disconnect handling in real-time
\end{itemize}

@@

\begin{itemize}
\item<1-> Divorces peripherals from the computers to which they are
  attached
\item<2-> Allows simple creation of a ``Device Server''
\item<3-> Extends the ``Everything Is A File'' -nix Philosophy
\item<4-> Allows more efficient use of devices
\item<5-> Allows devices to be networked in a generalized, uniform manner
\end{itemize}

@@

\begin{itemize}
\item<1-> Does not work well when Character Device is not the exclusive
  device interface
  \begin{itemize}
  \item Many modern day devices interface directly with other
    in-kernel function, interfaces, and APIs
  \item procfs and sysfs provide additional device interface points
  \item Socket interfaces (netlink, etc) provide alternative to file
    system interfaces
  \end{itemize}
\item<2-> Requires exported devices to be ``de-integrated'' from host system
\item<3-> Requires QOS guarantees and high guilty network connection
\end{itemize}

@@

\begin{itemize}
\item<1-> Quick, cheap, and simple ad-hoc network KVM systems
\item<2-> Remote, networked web-cams, scanners, printers, etc
\item<3-> Basis of ``protocol''-over-Ethernet systems (USB-over-Ethernet,
  SATA-over-Ethernet, Etc)
\item<4-> Basis of redundant, ``cloud-like'' device pools
\item<5-> Basis of peripheral cluster systems (GPU Clusters, RNG Clusters,
  Etc)
\end{itemize}

%---KVM Slide---%
\begin{frame}{\bf KVM}

Building a networked KVM system with NCDs:

  \begin{center}
    \includegraphics[height=0.6\paperheight,keepaspectratio]{kvm.png}
  \end{center}

%---Device Pool Slide---%
\begin{frame}{\bf Random Number Generator Pool}

Building a distributed RNG system with NCDs:

  \begin{center}
    \includegraphics[height=0.6\paperheight,keepaspectratio]{rng.png}
  \end{center}

@@

\begin{itemize}
\item<1-> Add multi-device, multi-server support
\item<2-> Add kernel sub-system handler layer (HID, etc)
\item<3-> Add device protection and removal capabilities to server system
\item<4-> Add advertisement protocol
\item<5-> Consider removing networking code from client kernel module
\end{itemize}

@@

%---Conclusion Slide---%
\begin{frame}{\bf Conclusion}

Network Character Devices provide:

\begin{itemize}
\item<1-> A simple means to add network functionality to devices using
  well understood file semantics and interfaces.
\item<2-> The groundwork for cloud-like device pools and arrays
\item<3-> The means to efficiently export devices from where they are not
  need and import them where they can be used.
\end{itemize}

But to make them widely applicable:

\begin{itemize}
\item<4-> Device drivers must move back toward the sole use of the
  device file based APIs
\item<5-> Advertisement and management tools must be added
\item<6-> The OS must not assume that it has exclusive access to any
  device connected to the physical hardware on which it is running.
\end{itemize}

\section{Bibliography}

%---Bibliography---%
\begin{frame}{\bf Bibliography}
